% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org

% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca

% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com

% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

\newlength{\outerbordwidth}

\pagestyle{empty}

\raggedbottom

\raggedright

\usepackage[svgnames]{xcolor}

\usepackage{framed}

\usepackage{tocloft}
\usepackage{xcolor}
\usepackage{etoolbox}

\usepackage[T1]{fontenc}
\usepackage[sfdefault]{biolinum}   %% Option 'sfdefault' only if
%% the base font of the document is to be sans serif

\robustify\cftdotfill

%-----------------------------------------------------------

%Edit these values as you see fit

\setlength{\outerbordwidth}{2pt}  % Width of border outside of title bars

\definecolor{shadecolor}{rgb}{0.8, 0.8, 0.9} % Outer background color of title bars (0 = black, 1 = white)

\definecolor{shadecolorB}{rgb}{0.95, 0.95, 1.0}  % Inner background color of title bars

\definecolor{darkred}{rgb}{0.5,0.0,0.0}  % Cornell's color

\definecolor{yelpcolor}{HTML}{AF0606}  % Yelp's color

\definecolor{linkedincolor}{HTML}{0976B4}  % LinkedIn's color

\definecolor{facebookcolor}{HTML}{3B5998}  % Facebook's color

\definecolor{noomcolor}{HTML}{FF8600}  % Noom's color

\definecolor{pinterestcolor}{HTML}{BD081C}  % Pinterest's color

\definecolor{gecolor}{HTML}{3A5DAE}  % GE's color

\definecolor{stitchfixcolor}{HTML}{00ABA9}  % Stitch Fix's color

\definecolor{nikecolor}{HTML}{BA2B2B}  % Nike's color

\definecolor{latlonglabscolor}{HTML}{00ACE1}  % Lat Long Labs' color

\definecolor{gold}{rgb}{1.0, 1.0, 0.0}  % Berkeley's color

\definecolor{deepblue}{rgb}{0.0, 0.0, 0.8}  % Berkeley's color

%-----------------------------------------------------------

%Margin setup

\setlength{\evensidemargin}{-0.25in}

\setlength{\headheight}{-0.25in}

\setlength{\headsep}{0in}

\setlength{\oddsidemargin}{-0.25in}

\setlength{\paperheight}{11in}

\setlength{\paperwidth}{8.5in}

\setlength{\tabcolsep}{0in}

\setlength{\textheight}{9.75in}

\setlength{\textwidth}{7in}

\setlength{\topmargin}{-0.3in}

\setlength{\topskip}{0in}

\setlength{\voffset}{0.1in}

%-----------------------------------------------------------

%Custom commands

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{\vspace{8pt}

  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}

    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}

    \end{shaded}

  }\vspace{-5pt}

}

\newcommand{\ressubheading}[4]{

\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}

		\textbf{#1} & #2 \\

		\textit{#3} & \textit{#4} \\

\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Dr. June Andrews} & \textbf{\today} \\

Portland, OR /\ San Francisco, CA & astuteajax@gmail.com \\

 & linkedin.com/in/DrAndrews \\

 & Cell: 415.906.9228

\end{tabular*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{TLDR}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

    \resitem{Built and led ML teams at three companies. Founded a startup for optimizing where to live.}
    \resitem{Developed strategies and roadmaps aligning company objectives, personnel growth, and tech feasibility.}
    \resitem{Track record of navigating research-level technical challenges and deploying solutions to production.}
    \resitem{Drawn to critical path challenges that require innovative data science, ML, or AI.}

 \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Research and Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item[] 
	\ressubheading{\color{latlonglabscolor}Lat Long Labs}{}{Founder}{2023 - 2024}

        \begin{itemize}
            \resitem{Founded Lat Long Labs to revolutionize the way people choose where to live.}
            \resitem{Pioneered breakthroughs in personalized financial modeling, creating the first Discretionary Income model tailored to occupation, experience, family composition, and zip code.}
            \resitem{Developed the first constraint optimization model for personalized location searches.}
            \resitem{Managed comprehensive startup responsibilities, including legal affairs, business strategy, investor pitches, product demos, customer interviews, and product-market fit adjustments.}
        \end{itemize}

	
\item[] 
	\ressubheading{\color{linkedincolor}LinkedIn}{}{Tech Lead}{2021 - 2023}

	\begin{itemize}
	    \resitem{Developed and led the {\it Good to Great to World Class} technical review program, increasing the impact, precision, and accuracy of over 50 data analysts, data scientists, data engineers, and ML engineers.}
            \resitem{Mentored emerging talent and coached data scientists through challenges.}
	\end{itemize}
 
\item[] 
	\ressubheading{\color{nikecolor}Nike}{}{Senior Director of Search Sciences}{2021}

	\begin{itemize}
	    \resitem{Stabilized and expanded the Search Sciences Team, consisting of 8 data scientists and ML engineers, responsible for search algorithms on nike.com routing over \$1B in purchasing power. Resolved development impasse and launched the first mobile experiment for Nike, leading to immediate revenue improvements in the millions.}
	\end{itemize}
	
	
\item[] 
	\ressubheading{\color{stitchfixcolor}Stitch Fix}{}{Data Science Manager - Style Discovery}{2019 - 2021}

	\begin{itemize}
	    \resitem{Led a team of 6 ML Engineers and Data Scientists, fostering cross-functional collaborations with Engineering, Merchandise, Strategy, Product, and Algorithms organizations. Our team revolutionized a fundamental fashion paradigm by integrating client feedback on designs with historical purchasing behavior, enabling predictive modeling of client responses to garments before manufacturing, at scale. This recommender system now informs decisions on individual garments, guides vendor relationships, tests growth trajectories, and enhances inventory growth efficiency.}
	    \resitem{Style Discovery contributed to the launch of the Elevate program, which utilized internal tools to assist emerging BIPOC designers in determining product market fit, planning supply chain volume, and optimizing B2C presentation.}
	    \resitem{Supported cross-organizational alignment for measuring and setting growth trajectories, transitioning from current Share of Market to Total Addressable Market.}
	\end{itemize}
	
\item[] 
	\ressubheading{\color{gecolor}Wise.io, from GE Digital}{}{Principal Data Scientist}{2017 - 2019}

	\begin{itemize}
	    \resitem{Led a collaboration of hundreds of people and a core ML team, across 7 time zones, launching machine learning for real-time airplane engine monitoring \& diagnostics. Deployed to all commercial jet engines monitored by GE.}
	    \resitem{Built key production ML components beating previously used state of the art.}
	    \resitem{Mentored Power Plant monitoring \& diagnostics initiatives inspired by aviation work.}
	\end{itemize}

\item[]
	\ressubheading{\color{deepblue}University of California, Berkeley}{}{Masters Program Lecturer in Applied Machine Learning}{2018 - 2019}
	\begin{itemize}
	    \resitem{Taught and mentored industry professionals on building ML products in their domains.}
	\end{itemize}

\item[] 
	\ressubheading{\color{pinterestcolor}Pinterest}{}{Data Scientist}{2015 - 2017}

	\begin{itemize}
	    \resitem{Created the Signal Program and Repository, a feature store used across the organization to design, evaluate, and experiment on adding new features into Ads, Growth, and Search production models. Program results were used and contributed to by 50+ machine learning engineers.}
	\end{itemize}

	
\item[] 
	\ressubheading{\color{linkedincolor}LinkedIn}{}{Staff Data Scientist \& Tech Lead}{2013 - 2015}

	\begin{itemize}
	
		\resitem{Helped hire, onboard, and grow a team of 11 data scientists working on consumer analytics.}
		
		\resitem{Worked with Growth Team to systematically identify, scope and experimentally test data driven outreach campaigns. Hit or exceeded member growth targets for 8 quarters.}
		
		\resitem{Used social networks background in developing products, analysis, and prototypes focused on user engagement, viral content, and network health.}

		
	\end{itemize}

\item[] 
	\ressubheading{\color{yelpcolor}Yelp Inc}{}{Search and Data Engineer}{2012 - 2013}

	\begin{itemize}
		\resitem{Built data pipelines, metrics, and ran experiments for Search Ranking, and User Engagement}

		\resitem{Built Yelp's first Query Normalization, Human Eval of Search Results, and Personalized Search}

	\end{itemize}


\item[]

	\ressubheading{\color{facebookcolor}Facebook Inc}{}{Growth and Product Insights Intern}{Summer 2011}

	\begin{itemize}

		\resitem{Analyzed acceleration and deceleration of user engagement with Facebook}

	\end{itemize}


\item[]
	\ressubheading{\color{darkred}Cornell University}{}{Networks Research with Prof. John Hopcroft }{2010-2012}

	\begin{itemize}

		\resitem{Researched and computed structure of communities in large networks. Studied evolution and flow of information between communities in social, collaborative, and similarity networks.}

	\end{itemize}

	\ressubheading{}{}{Head Teaching Assistant for Java and Discrete Math (600+ students \& 27 TAs)}{2011 - 2012}

	\ressubheading{}{}{Lecturer for Functional Programming and Data Structures ($2^{nd}$ foundational course)}{2010}

\item[] 

	\ressubheading{\color{deepblue}University of California, Berkeley}{}{Research Assistant with Prof. James Sethian for PDE research}{2005-2007}

\item[]

	\ressubheading{\color{darkred}San Diego Supercomputer Center}{}{NSF REU Research Assistant under Amit Majumdar for parallel data transfer}{Summer 2005}


\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item[]

	\ressubheading{{\color{darkred}Cornell University}}{Ithaca, NY}{Ph.D. Applied Math, M.S. Applied Math, emph in Social Networks}{2007 - 2012}

\item[]

	\ressubheading{{\color{deepblue}University of California, Berkeley}}{Berkeley, CA}{B.Sc. Electrical Engineering and Computer Science, minor in Applied Math}{2003 - 2007}


\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item[] {\bf Unique Signature:} Developing ML Platforms in critical paths, including setting strategy, crafting architecture, and building teams.

\item[] {\bf Management:} ML Strategy, Talent Development, Recruiting pipelines, Cross Functional Alignment

\item[]{\bf Prior Development:}  Python(advanced), Spark, Presto, Pig, Java, Hive, Hadoop, C, MPI, R

\item[] {\bf Network Analysis:} Community Detection, Structure of large networks, Network Cascades

\item[] {\bf Numerical Analysis:} Optimization, PDEs, Linear Algebra, Iterative and Non-Iterative Methods

\item[] Diverse background in Mathematics, Computer Science, and leadership facilities the swift acquisition of new skills.

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Selected Talks and Publications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

	\item[] \ressubheading{MLConf - Speaker}{}{The Uncanny Valley of ML}{2019}
	
	\item[] \ressubheading{MLConf - Speaker}{}{Counter Intuitive Machine Learning for the Industrial Internet of Things}{2017}
	
	\item[] \ressubheading{Strata NY - Featured Speaker}{}{Replication in Data Science}{2016}
	
	\item[] \ressubheading{Strata San Jose - Featured Speaker}{}{Economic Insights from the LinkedIn Network}{2015}

	\item[] \ressubheading{PNAS - Author}{}{Fast Marching Methods for the continuous Traveling Salesman Problem}{2007}


\end{itemize}


\resheading{Hobby Data Science Projects}

\begin{itemize}

\item[] {\bf Academic Relations [2015-current]: }{National Science Foundation and ARPA-E panels, UC Berkeley Extension Board and teaching classes for UC Berkeley School of Information's Master in Data Science program.}

\item[] {\bf Emerging Speakers in Tech [2015-2017]:} Created a supportive community for conference speakers.

\item[] {\bf Additional:} Book reviews for O'Reilly Media and mentoring data scientists.
\end{itemize}

\end{document}

